---
title: "Coding Assignment 1"
author: "Group 7: Kim Dove, Daniel Arbelaez, Anita Gabbard, Mohammad Amori"
date: "Due: 2022-09-25 23:59"
output:
  html_document:
    toc: yes
    toc_depth: 2
    toc_float: yes
  word_document:
    toc: yes
    toc_depth: '2'
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages, include=TRUE}
# Put any packages you want here
library(gt)
library(tidyverse)
library(gtsummary)
library(plotly)
library(readxl)
library(plotly)
library(corrplot)
library(dplyr)
library(car)
library(jtools)
sessionInfo()
```


A Florida health insurance company wants to predict annual claims for individual clients. The company pulls a random sample of 50 customers. The owner wishes to charge an actuarially fair premium to ensure a normal rate of return. The owner collects all of their current customer’s health care expenses from the last year and compares them with what is known about each customer’s plan. 

The data on the 50 customers in the sample is as follows:

-	Charges: Total medical expenses for a particular insurance plan (in dollars)
-	Age: Age of the primary beneficiary
-	BMI: Primary beneficiary’s body mass index (kg/m2)
-	Female: Primary beneficiary’s birth sex (0 = Male, 1 = Female)
-	Children: Number of children covered by health insurance plan (includes other dependents as well)
-	Smoker: Indicator if primary beneficiary is a smoker (0 = non-smoker, 1 = smoker)
-	Cities: Dummy variables for each city with the default being Sanford

Answer the following questions using complete sentences and attach all output, plots, etc. within this report.


**For this assignment, ignore the categorical variables (gender, smoker, cities)**

```{r dataset, include=TRUE}
# Bring in the dataset here
insurancegroup7 <- read_excel("../Data/insurance_0126_Group7.xlsx")

```

```{r global function}
# Custom function created by professor to generate the mode using the "charges" variable
getModes <- function(x) {
  ux <- unique(x)
  tab <- tabulate(match(x, ux))
  ux[tab == max(tab)]
}

```

# Question 1

Perform univariate analyses on the quantitative variables (center, shape, spread). Include descriptive statistics, and histograms. Be sure to use terms discussed in class such as bimodal, skewed left, etc.

```{r q1 Charges}
# ************************************* CHARGES  *************************************

# Adding the Charges column to the "Charges" variable
Charges <- (insurancegroup7$Charges)
# Summary of descriptive statistics including Mean, Median, IQR, Min, Max
summary(Charges)
#Standard Deviation
sd(Charges)
# Using the custom function from the professor to get the mode of the Charges column using the "charges" variable
getModes(Charges)
IQR(Charges)
# Generate a histogram of the Charges column using the "charges" variable
hist(Charges)
```
<br>Mean: 15132.46 <br>
Median: 9819.649<br>
Mode: Unimodal<br>
Std Deviation: 14569.33<br>
Histogram: Skewed right, wide distribution <br>
Measure of center: Median is not sensitive to outliers while the mean is, thus Median better used as the measure of center in Charges. 
Measure of spread: Standard deviation is sensitive to outliers since it measures the distance between the data point and the mean. Additionally, the range is also sensitive to outliers, range: 58,571 – 1,147 = 57,424. In this case, because the mean is not the center the interquartile range (Q3-Q1)may be a better measure of spread because it is not sensitive to outliers. The interquartile range:  20,372 - 4,144 = 16,288.
<br>

```{r q1 Age}
# ************************************* Age  *************************************

Age <- (insurancegroup7$Age)
summary(Age)
sd(Age)
getModes(Age)
hist(Age)

```
<br>Mean:           37.56 <br>
Median:         36.00<br>
Mode:           Bimodal<br>
Std Deviation:  14.81196<br>
Histogram:      Bimodal, two peaks<br>
Measure of center: Mean<br>
Measure of spread:  Since the Mean is the measure of center the best measure of spread will be the standard deviation (14.81196)<br>
```{r q1 BMI}
# ************************************* BMI  *************************************

BMI <- (insurancegroup7$BMI)
summary(BMI)
sd(BMI)
getModes(BMI)
hist(BMI)
```
<br>Mean: 32.33<br>
Median: 32.11<br>
Mode: Bimodal<br>
Std Deviation:5.150382<br>
Histogram: Bell shaped curve<br>
Measure of center: Since the histogram takes on a bell shaped curve the mean is the preferred measure of center.<br>
Measure of spread: With a bell shaped curve histogram the best measure of spread is the standard deviation.
 
```{r q1 Children}
# ************************************* Children  *************************************

Children <- (insurancegroup7$Children)
summary(Children)
sd(Children)
getModes(Children)
hist(Children)
IQR(Children)

```
<br>Mean: 1.06<br>
Median: 1.00<br>
Mode: 0<br>
Std Deviation:1.391079<br>
Histogram: Skewed right, Unimodal<br>
Measure of center: Median<br>
Measure of spread: IQR (1.75)



# Question 2

Perform bivariate analyses on the quantitative variables (direction, strength and form). Describe the linear association between all variables. 

```{r q2}
#use cor and scatterplot function
data <- data.frame(Charges, Age, BMI, Children)
scatterplotMatrix(data)

corrplot(cor(data),
         type = "lower",order = "hclust",
         tl.col = "black",
         tl.srt = 45,
         addCoef.col = "black",
         diag = FALSE,)

```

<br>
None of the variables observe any strong positive or negative relationships, only weak linear relationships. The most significant relationship is between Age and BMI with a -.34 correlation.  The correlation coefficient “r” measures the strength of a relationship and is always a number between -1 and 1, values less than .3 = none or very week relationship, values between 0.3 and 0.5 = weak relationship, values between 0.5 and 0.7 = moderate relationship, values greater than 0.7 = strong relationship, values = +/- 1 = perfect linear relationship. Correlation  provides insight into the relationship between variables and is NOT causation. <br>

# Question 3

Generate a regression equation in the following form:

$$Charges = \beta_{0}+\beta_{1}*Age+\beta_{2}*BMI+\beta_{3}*Children$$

```{r q3}
model_Charges <- lm(Charges~Age + BMI + Children, data = insurancegroup7)
model_Charges
summary(model_Charges)
summ(model_Charges)
```

also write out the regression cleanly in this document.

$$ Multiple Linear Regression for Charges = -14772 + 247*Age + 601*BMI + 1129*Children $$

# Question 4

An eager insurance representative comes back with a potential client. The client is 40, their BMI is 30, and they have one dependent. Using the regression equation above, predict the amount of medical expenses associated with this policy. (Provide a 95% confidence interval as well)


```{r q4}
newPrediction <- data.frame(Age = 40, BMI = 30, Children = 1)
predict(model_Charges, newdata = newPrediction, interval = "confidence")

```
<br> A person of age 40 with a BMI of 30 and 1 child will have medical expenses around $14,269.15. Using a 95% confidence interval the prediction has a lower limit of $9,678.64 and an upper limit of $18,859.66.<br>