---
title: "Coding Assignment 2"
author: "Team 7"
date: "Due: 2022-10-23 23:59"
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=TRUE}
#Put any packages you need here
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages, include=TRUE}
# Put any packages you want here
library(gt)
library(tidyverse)
library(gtsummary)
library(plotly)
library(readxl)
library(plotly)
library(corrplot)
library(dplyr)
library(car)
library(jtools)
sessionInfo()
```
A Florida health insurance company wants to predict annual claims for individual clients. The company pulls a random sample of 50 customers. The owner wishes to charge an actuarially fair premium to ensure a normal rate of return. The owner collects all of their current customer’s health care expenses from the last year and compares them with what is known about each customer’s plan. 

The data on the 50 customers in the sample is as follows:

-	Charges: Total medical expenses for a particular insurance plan (in dollars)
-	Age: Age of the primary beneficiary
-	BMI: Primary beneficiary’s body mass index (kg/m2)
-	Female: Primary beneficiary’s birth sex (0 = Male, 1 = Female)
-	Children: Number of children covered by health insurance plan (includes other dependents as well)
-	Smoker: Indicator if primary beneficiary is a smoker (0 = non-smoker, 1 = smoker)
-	Cities: Dummy variables for each city with the default being Sanford

Answer the following questions using complete sentences and attach all output, plots, etc. within this report.


```{r dataset, include=FALSE}
# Bring in the dataset here
insurancegroup7 <- read_excel("../Data/insurance_0126_Group7.xlsx")
```



## Question 1

Generate this regression equation:

$$Charges = \beta_{0}+\beta_{1}*Age+\beta_{2}*BMI+\beta_{3}*Children + \beta_{4}*Female + \beta_{5}*Smoker + \beta_{6}*WinterSprings + \beta_{7}*WinterPark + \beta_{8}*Oviedo$$

```{r q1}
model_Charges <- lm(Charges~., data = insurancegroup7)
summary(model_Charges)

```
$$ Charges = -17221 + 217*Age + 389*BMI + 2653*Female + 1423*Chidren + 29037*Smoker + 4013*WinterSprings + 2304*WinterPark + 2008*Oviedo $$

Which independent variables test significant in a two-tailed test? Use $\alpha = 0.2$

The following independent variables test significant in a two-taled test against an alpha of .2:<br>
1. Age<br>
2. BMI<br>
3. Female<br>
4. Children<br>
5. Smoker<br>
6. WinterSprings<br>

## Question 2

Interpret the coefficients of all the independent variables that tested significant.<br><br>

**Age:** Every year adds $217 to the charges for the medical plan<br>
**BMI:** Every point adds $389 to the charges for the medical plan<br>
**Female:** Being a female is $2,653 more expensive than being a man on this plan<br>
**Children:** Each adds $1423 to the charges for the medical plan<br>
**Smoker:** Being a smoker is $29,037 more expensive than being a non-smoker<br>
**WinterSprings:** Living in WinterSprings is $4,013 more expensive than living in Sanford for this plan. Comparing against the other cities (Winter Park and Oviedo) isn't possible as their relationship is insignificant.<br><br>

## Question 3

The insurance agent returns with another client:

- Age: 35
- BMI: 26
- Children: 1
- Gender: Female
- Smoker: No
- City: Sanford

Using the regression equation above, predict the amount of medical expenses associated with this policy. (Provide a 95% confidence interval as well)

```{r q3}
newPrediction <- data.frame(Age = 35, BMI = 26, Children = 1, Female = 1, Smoker = 1, WinterSprings = 0, WinterPark = 0, Oviedo = 0)

predict(model_Charges, newdata= newPrediction, interval = "confidence")
```
##### Based on the prediction model the charges for a 35 year old Female living in Sanford who smokes with a BMI of 36 and has a child will be $33,600 give or take $6,000.


## Question 4

Compare the model from question 1, to a model that does not include the group of city dummies. Does including the cities reduce the SSE by a statistically significant amount? (check the partial F-test for significance of the dummies as a group). Use $\alpha = 0.05$

```{r q4}
dummy_free <- insurancegroup7[,1:6, drop=FALSE] 
dummy_free <- lm(Charges ~., data = dummy_free)
summary(dummy_free)
anova(dummy_free, model_Charges)
```


